Discrete Probability for Discrete Quantum Theories

### 2016-05-07 prob.tex
buffon nice

These resource considerations thus lead us to replace the real
interval $[0,1]$ with intervals of confidence which contain the
probability. The intuition is that the precision of the interval will
depend on the amount of resources allocated for the measurement.

>>>>

These resource considerations thus lead us to replace the real
interval $[0,1]$ with rational numbers up to a certain precision.  The
intuition is that the precision depends on the amount of resources
allocated for the measurement process.

There is however another more subtle source of unbounded computational
power in the experiment. We are assuming that we can always determine
with certainty whether a needle is crossing a line. But ``lines'' on
the the floor have thickness, their distance apart is not exactly
$\ell$. and the needles lengths are not all equal and are not all
absolutely equal to $\ell$. These perturbations make the events
``fuzzy.'' For example, instead of talking about the idealized event
that exactly $M$ needles cross lines, we might instead talk about the
event that $M-\delta$ needles evidently cross lines and $M+\delta'$
needles plausibly cross lines. This fuzzy notion of events leads us to
consider intervals of probability reflecting the certainty of the
event and its plausibility.
